### 2017-07-07 implementation.tex
Edits.

\textbf{Annotation Burden} \tool significantly reduces the annotation
burden in verifying a weakly isolated transactions by eliminating the
need to annotate intermediary assertions and loop invariants.
Guarantees ($G$) and invariants ($I$), however, still need to be
provided. Alternatively, a weakly isolated transaction $T$ can be
verified against the generic serializability condition, to eliminate
the need for any annotation. In this mode, \tool first infers the
transformer $\F_{SER}$ of $T$ without considering any interference,
which then becomes its guarantee ($G$). Doing likewise for every
transaction results in a rely relation ($R$) that includes $\F_{SER}$
of every transaction. The verification can now proceed as usual. The
result of this verification is an assignment of (possibly weak)
isolation levels to transactions which guarantees serializability of
all executions.

>>>>

\textbf{Annotation Burden} \tool significantly reduces the annotation
burden in verifying a weakly isolated transactions by eliminating the
need to annotate intermediary assertions and loop invariants.
Guarantees ($G$) and invariants ($I$), however, still need to be
provided. Alternatively, a weakly isolated transaction $T$ can be
verified against the generic serializability condition, to eliminate
the need for any annotation. In this mode, \tool first infers the
transformer $\F_{SER}$ of $T$ without considering any interference,
which then becomes its guarantee ($G$). Doing likewise for every
transaction results in a rely relation ($R$) that includes $\F_{SER}$
of every transaction. Verification now proceeds by taking interference
into account, and verifying that each transaction still yeilds the
same $F$ as its $F_{SER}$. The result of this verification is an
assignment of (possibly weak) isolation levels to transactions which
nonetheless guarantees serializability of all executions.
